---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
        fig.path="man/figures/"
)
```

# spatialWeights

[![Build Status](https://travis-ci.org/christophergandrud/spatialWeights.svg?branch=master)](https://travis-ci.org/christophergandrud/spatialWeights)

This R package is designed to implement some of the spatial weights for time series cross sectional data discussed in 
[Neumayer and Plumper (2010)](http://eprints.lse.ac.uk/30750/1/Making%20spatial%20analysis%20operational(lsero).pdf).

Weights can be found in parallel for improved speed.

## Examples

### Data with spatial clustering

Here is a simple example with fake data with spatial clustering:

```{r}
library(spatialWeights)

# Create fake time series data
faked1 <- expand.grid(ID = letters, year = 2010:2015)
faked1$located_continuous <- nrow(faked1):1
faked1$y <- nrow(faked1):1 - 200

# Find weights for continuous data
df_weights_cont1 <- monadic_spatial_weights(df = faked1, id_var = 'ID',
                                         time_var = 'year',
                                         location_var = 'located_continuous',
                                         y_var = 'y', mc_cores = 1)

summary(df_weights_cont1)
```

### Data without spatial clustering

```{r}
# Create fake time series data
faked2 <- expand.grid(ID = letters, year = 2010:2015)
faked2$located_continuous <- rnorm(nrow(faked2)) 
faked2$y <- nrow(faked2):1 - 200

# Find weights for continuous data
df_weights_cont2 <- monadic_spatial_weights(df = faked2, id_var = 'ID',
                                         time_var = 'year',
                                         location_var = 'located_continuous',
                                         y_var = 'y', mc_cores = 1)
```

### Temporally Lagged Spatial Lags

By default `monadic_spatial_weights` creates a spatially lagged variable. Using the arguement `tlsl = TRUE` will lag this variable in time by one period creating a time lag spatial lag. For example:  

```{r}
# Create fake time series data
faked1 <- expand.grid(ID = letters, year = 2010:2015)
faked1$located_continuous <- nrow(faked1):1
faked1$y <- nrow(faked1):1 - 200

# Find weights for continuous data
df_weights_cont_tlsl <- monadic_spatial_weights(df = faked1, id_var = 'ID',
                                         time_var = 'year',
                                         location_var = 'located_continuous',
                                         y_var = 'y', mc_cores = 1, tlsl = TRUE)

head(df_weights_cont_tlsl)
```

## Install

The package can be installed with:

```{r, eval=FALSE}
devtools::install_github("christophergandrud/spatialWeights")
```
